\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-22 notes/2loopNLSM.tex

In fact, we can make the failure extremely precise.  Start with the
diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
the double-box, crossed-box, and penta-triangle.  For each of the
three diagrams, write down the most generic parity-even local ansatz
involving four polarizations and six momenta (any combination of
external or loop).  Each ansatz will have 10,010 terms initially.  Next
impose the symmetry constraints on each of the three diagrams, leaving
2,761 free parameters on the double-box, 2,576 free parameters on the
crossed-box, and 5,040 free paramters on the penta-triangle.  Then
impose the ``bowtie'' next-to-maximal cut, which in the
\emph{non-planar} $t$-$u$ color channel only recieves contributions
from the double-box
\begin{equation}
   \NMCutC
  =
  \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
  N \left[
    \KTDBContrib{1}{2}{3}{4}
  \right]
  +
  \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
  N\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
\end{equation}
After imposing this cut, we find that the original Jacobi relation,
\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
\begin{eBox}
\begin{equation}\label{chefsKiss}
   \NMCutC
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
\end{eBox}
Thus we have identified the minimal failure state for a
globally-color-dual two-loop Yang-Mills representation: locality,
symmetry, and the kinematic Jacobi relations for just three diagrams
are incompatible with the ``bowtie'' cut.

@@

Using this, we can redefine the non-local numerators of \cref{nonLocalNum} so that the vector structure of YM is captured in a permutation invariant prefactor and the kinematic Jacobi identity is entirely due to the NLSM numerators
\be
N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s_{12}s_{23}s_{13}} \, .
\ee
One advantage of this construction is that it reduces some of the $D$-dimensional complexity of vector theories that arises due to the mixing between external polarization and
internal loop momenta. But maybe more importantly, it puts all the heavy lifting of functional Jacobi relations on the scalar kinematic numerator, $N_{(12|34)}^{\text{NLSM}}$. Thus, rather
than building an ansatz from the irreducible scalar products of
\cref{eq:ym-basis}, one might instead consider the following construction
\begin{equation}
N^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
\end{equation}
where $\mathcal{O}_i$ are the on-shell gauge invariant tensor basis elements of
\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ are
rational functions of irreducible scalar products of \cref{eq:scalar-basis}. It would be interesting if a similar construction as our tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work. We see this as a natural future direction worth investigating that is made possible given our findings.

>>>>

In fact, we can make the failure extremely precise.  Start with the
diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
the double-box, crossed-box, and penta-triangle.  For each of the
three diagrams, write down the most generic parity-even local ansatz
involving four polarizations and six momenta (any combination of
external or loop).  Each ansatz will have 10,010 terms initially.  Next
impose the symmetry constraints on each of the three diagrams, leaving
2,761 free parameters on the double-box, 2,576 free parameters on the
crossed-box, and 5,040 free paramters on the penta-triangle.  Then
impose the ``bowtie'' next-to-maximal cut, which in the
\emph{non-planar} $t$-$u$ color channel only recieves contributions
from the double-box
\begin{equation}
   \NMCutC
  =
  \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
  N \left[
    \KTDBContrib{1}{2}{3}{4}
  \right]
  +
  \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
  N\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
\end{equation}
After imposing this cut, we find that the original Jacobi relation,
\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
\begin{eBox}
\begin{equation}\label{chefsKiss}
   \NMCutC
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
\end{eBox}
Thus we have identified the minimal failure state for a
globally-color-dual two-loop Yang-Mills representation: off-shell locality,
symmetry, and the kinematic Jacobi relations for just three diagrams
are incompatible with the ``bowtie'' cut.

@@

Using this, we can redefine the non-local numerators of \cref{nonLocalNum} so that the vector structure of YM is captured in a permutation invariant prefactor and the kinematic Jacobi identity is entirely due to the NLSM numerators
\be
N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s_{12}s_{23}s_{13}} \, .
\ee
One advantage of this construction is that it reduces some of the $D$-dimensional complexity of vector theories that arises due to the mixing between external polarization and
internal loop momenta. But maybe more importantly, it puts all the heavy lifting of functional Jacobi relations on the scalar kinematic numerator, $N_{(12|34)}^{\text{NLSM}}$. Thus, rather
than building an ansatz from the irreducible scalar products of
\cref{eq:ym-basis}, one might instead consider the following construction
\begin{equation}
N^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
\end{equation}
where $\mathcal{O}_i$ are the on-shell gauge invariant tensor basis elements of
\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ are
rational functions of irreducible scalar products of \cref{eq:scalar-basis}. It would be interesting if a similar construction as our tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work. We see this as a natural future direction worth investigating that is now made possible by our findings.
